Ecology and Conservation Modelling Preregistration Template -- DRAFT

### 2020-05-19 analysis/preregistration_template.Rmd
Update analysis/preregistration_template.Rmd
Fix typo
Fix #13 Respond to Meg's comments on variables

## 2.3-define_conceptual_model: identify predictor response variables

@@

- *What variables would support taking this action or making this decision?* 
- *What additional variables may interact with this system (things we can't control, but can hopefully measure).* 
- *In what ways do we expect these variables to interact (model structures).* 
Should you include variables that haven't been measured and that might also interact with the system (not ideal, but this happens in field studies). Possibly also variables that are assumed to be a surrogate measure of variables that we can't or haven't measured.

@@

*Describe any data preparation and processing steps, including manipulation of environmental layers, e.g. standardisatino and geographic projection.* Something about always retaining the raw data in a safe place, no manipulations to the raw file.

>>>>

## 2.3 Define conceptual model: identify predictor response variables

@@

- *What variables would support taking this action or making this decision?* 
- *What additional variables may interact with this system (things we can't control, but can hopefully measure)?*
- *What variables have not been measured, but may interact with the system (often occurs in field or observational studies)?*
- *What variables are indice or surrogate measures of variables that we cannot or have not measured?*
- *In what ways do we expect these variables to interact (model structures)?*

@@

*Describe any data preparation and processing steps, including manipulation of environmental layers, e.g. standardisation and geographic projection.* Something about always retaining the raw data in a safe place, no manipulations to the raw file.
